---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## 0. Loading and preprocessing the data
```{r, echo = TRUE}
# reading the file
act_data <- read.csv("activity.csv")
# open libraries
library(plyr)
library(ggplot2)
library(scales)
# pre-processing
# total steps per day
steps_day <- ddply(act_data, .(date), summarise, sum.steps = sum(steps, na.rm = TRUE))
# mean steps per five minute interval across all days
steps_int <- ddply(act_data, .(interval), summarise, mean_steps = mean(steps, na.rm = TRUE))
```


## 1. What is mean total number of steps taken per day?
1.1 Make a histogram of the total number of steps taken each day.

```{r, echo = TRUE}
act_data$date <- as.Date(act_data$date)
act_data$steps <- as.double(act_data$steps)
qplot(act_data$date, y=act_data$steps, geom="histogram", binwidth = 61, stat="identity",
      xlab = "Date", ylab = "Total steps per day", 
      main = "Total Number Of Steps Taken Each Day")
```

1.2 Calculate the mean and median total number of steps taken per day

Mean steps per day
```{r, echo = TRUE}
mean(steps_day$sum.steps, na.rm = TRUE)
```

Median steps per day
```{r, echo = TRUE}
median(steps_day$sum.steps, na.rm = TRUE)
```

## 2. What is the average daily activity pattern?
2.1 A time series plot (type = "l" ) of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days.

```{r, echo = TRUE}
# plot of average steps per interval
plot(steps_int$interval, steps_int$mean_steps, type = "l",
     main = "Average Daily Activity Pattern",
     xlab = "Five minute intervals in 24 hours of the day",
     ylab = "Average number of steps")
```

## 3. Imputing missing values



## 4. Are there differences in activity patterns between weekdays and weekends?
